\subsection{Server-side API}
The untrusted server implements:
\vspace{1em}

\api {\setup}$(1^\lambda, \upperbound) \rightarrow \pp, \vk$.
Randomized algorithm that returns public parameters $\pp$ used by the server and a \textit{verification key} $\vk$ used by clients.
Here, $\lambda$ is a security parameter and $\upperbound$ is an upper-bound on the number of elements $n$ in the dictionary (i.e., $n \le \upperbound$).

\api {\append}$(\pp, \AD_i, d_i, k,v) \rightarrow \AD_{i+1}, d_{i+1}$.
Deterministic algorithm that appends a new key-value pair $(k,v)$ to the version $i$ dictionary, creating a new version $i+1$ dictionary.
Succeeds only if the dictionary is not full (i.e., $i + 1 \le \upperbound$).
Returns the new authenticated dictionary $\AD_{i+1}$ and its digest $d_{i+1}$.

\api $\provelookup(\pp, \AD_i, k) \rightarrow V, \pi_{k,V}$.
Deterministic algorithm that generates a proof $\pi_{k,V}$ that $V$ is the \textit{complete} multiset of values for key $k$.
In particular, when $\AD_i(k) = \varnothing$, this is a proof that key $k$ has no values.
Finally, the server cannot construct a fake proof $\pi_{k,V'}$ for the wrong $V'$, including for $V' = \varnothing$.

\api {\proveappendonly}$(\pp, \AD_i, \AD_j) \rightarrow \pi_{i, j}$.
Deterministic algorithm that proves $\AD_i$ is a subset of $\AD_j$.
Generates an \textit{append-only proof} $\pi_{i, j}$ that all key-value pairs in $\AD_i$ are also present and unchanged in $\AD_j$.
Importantly, a malicious server who removed or changed keys from $\AD_j$ that were present in $\AD_i$ cannot construct a valid append-only proof.

\subsection{Client-side API}
Clients implement:
\vspace{1em}

\api {\verlookup}$(\vk, d_i, k, V, \pi) \rightarrow \{T, F\}$.
Deterministic algorithm that verifies proofs returned by $\provelookup(\cdot)$ against the digest $d_i$ at version $i$ of the dictionary.
When $V \ne \varnothing$, verifies that $V$ is the complete multiset of values for key $k$, ensuring no values have been left out and no extra values were added.
When $V = \varnothing$, verifies that key $k$ is not mapped to any value.

\api {\verappendonly}$(\vk, d_i, i, d_j, j, \pi_{i,j}) \rightarrow \{T, F\}$.
Deterministic algorithm that ensures a dictionary remains append-only.
Verifies that $\pi_{i,j}$ correctly proves that the dictionary with digest $d_i$ is a subset of the dictionary with digest $d_j$.
Also, verifies that $d_i$ and $d_j$ are digests of dictionaries at version $i$ and $j$, respectively.

\subsection{Correctness and Security}
Consider an ordered sequence of $n$ key-value pairs $(k_i\in \mathcal{K}, v_i\in\mathcal{V})_{i\in [n]}$.
Note that the same key (or key-value pair) can occur multiple times in the sequence.
% --- begin multiline ---
Let
$\AD',d' \leftarrow \multiappend(\pp, \AD, d, (k_i, v_i)_{i\in [n]})$
denote a sequence of $\append(\cdot)$ calls arbitrarily interleaved with other $\provelookup(\cdot)$ and $\proveappendonly(\cdot)$ calls such that
$\AD',d'$ $\leftarrow$ $\append(\pp,\AD_{n-1}, d_{n-1}, k_{n}, v_n)$,
$\AD_{n-1}, d_{n-1}$ $\leftarrow$ $\append(\pp,\AD_{n-2}$, $d_{n-2}, k_{n-1}, v_{n-1})$,
$\dots$,
$\AD_{1}, d_1$ $\leftarrow$ $\append(\pp,\AD, d, k_{1}, v_{1})$.
% --- end of multiline ---
Let $D_n$ denote the \textit{corresponding dictionary} obtained after appending each $(k_i, v_i)_{i\in [n]}$ in order.
%In other words, $\kv{k,v}\in D_n \Leftrightarrow \exists i\in [n]$ s.t. $k=k_i$ and $v=v_i$.
Finally, let $\AD_0$ denote an empty authenticated dictionary with (empty) digest $d_0$.

\begin{definition}[Append-only Authenticated Dictionary]
    \label{d:secure-maad-definition}
    (\setup, \append, \provelookup, \proveappendonly, \verlookup, \verappendonly) is a secure append-only authenticated dictionary (AAD) if
    $\forall$ upper-bounds $\upperbound=\poly(\lambda)$ it satisfies the following properties:
\end{definition}

\begin{definition}[AAD Lookup Correctness]
\label{def:aad:lookup-correctness}
$\forall n \le \upperbound$, $\forall$ sequences $(k_i\in \mathcal{K}, v_i\in\mathcal{V})_{i\in [n]}$ with corresponding dictionary $D_n$, $\forall$ keys $k\in\mathcal{K}$,
\begin{align*}
\Pr \left[ \begin{array}{c}
    (\pp,\vk) \leftarrow \setup(1^\lambda, \upperbound),\\
    (\AD, d) \leftarrow \multiappend(\pp, \AD_0, d_0, (k_i, v_i)_{i\in [n]}),\\
    (V, \pi) \leftarrow \provelookup(\pp,\AD, k): \\
    {V = D_n(k)} \wedge {\verlookup(\vk, d, k, V,\pi) = T}
\end{array} \right] \ge 1 - \negl(\lambda)
\end{align*}
\end{definition}

\noindent \textit{Observation:}
Note that this definition compares the returned multiset $V$ with the ``ground truth'' in $D_n$ and thus provides lookup correctness.
Also, it handles non-membership correctness since $V$ can be the empty set.
Finally, the definition handles all possible orders of inserting key-value pairs.

\begin{definition}[AAD Lookup Security]
\label{def:aad:lookup-security}
$\forall$ adversaries \Adv running in time $\poly(\lambda)$,
\begin{align*}
\Pr \left[ \begin{array}{c}
    (\pp,\vk) \leftarrow \setup(1^\lambda, \upperbound), \\
    (d, k,V\ne V',\pi,\pi') \leftarrow \Adv(1^\lambda, \pp, \vk)
    : \\
    {\verlookup(\vk,d, k,V,\pi) = T} \wedge {} \\
    {\verlookup(\vk,d, k,V',\pi') = T}
\end{array} \right] \le \negl(\lambda)
\end{align*}
\end{definition}

\noindent \textit{Observation:}
This definition captures the lack of any ``ground truth'' about what was inserted in the dictionary, since there is no trusted source in our model.
Nonetheless, given a fixed digest $d$, our definition prevents \textit{all} equivocation attacks about the complete multiset of values of a key, including the special case where the server equivocates about the key being present (i.e., $V \ne \varnothing$ and $V' = \varnothing$).
% Note that this definition also implies that different dictionaries cannot have the same digest.
% Suppose I have two different dictionaries with the same digest.
% Then, there must a key k with different multisets V and V'.
% Membership correctness says proofs for V and V' can be constructed w.r.t. to the digest.
% However, this breaks membership security.

\begin{definition}[AAD Append-only Correctness]
\label{def:aad:appendonly-correctness}
$\forall n \le \upperbound$, $\forall$ sequences $(k_i\in \mathcal{K}, v_i\in\mathcal{V})_{i\in [n]}$ where $n\ge 2$
\begin{align*}
\Pr \left[ \begin{array}{c}
    (\pp,\vk) \leftarrow \setup(1^\lambda, \upperbound) \\
    (\AD_m, d_m) \leftarrow \multiappend(\pp,\AD_0,d_0,(k_i, v_i)_{i\in [m]}),\\
    (\AD_n, d_n) \leftarrow \multiappend(\pp,\AD_m,d_m,(k_j, v_j)_{j\in [m+1,n]}),  \\
    \pi \leftarrow \proveappendonly(\pp,\AD_m, \AD_n):\\
    {\verappendonly(\vk, d_m, m, d_n, n, \pi) = T}
\end{array} \right] \ge 1 - \negl(\lambda)
\end{align*}
\end{definition}

% Note: This does not subsume lookup security when i = j because, according to this definition, V = [v1] and V' = [v1,v2] would both be allowed as the multisets for key k in the same digest d_i
\begin{definition}[AAD Append-only Security]
\label{def:aad:appendonly-security}
$\forall$ adversaries \Adv running in time $\poly(\lambda)$,
\begin{align*}
\Pr \left[ \begin{array}{c}
    (\pp,\vk) \leftarrow \setup(1^\lambda, \upperbound)\\
    (d_i,d_j,i<j,\pi_a, k,V\ne V',\pi,\pi') \leftarrow \Adv(1^\lambda, \pp, \vk)
    : \\
    {\verappendonly(\vk, d_i, i, d_j, j, \pi_a) = T} \wedge {}\\
    {\verlookup(\vk, d_i, k, V , \pi )  = T} \wedge {}\\
    {\verlookup(\vk, d_j, k, V', \pi') = T}
\end{array} \right] \le \negl(\lambda)
\end{align*}
\end{definition}

\noindent \textit{Observation:}
This definition ensures that values can only be added to a key and can never be removed nor changed.

\begin{definition}[AAD Fork Consistency]
This definition stays the same as for an AAS (see \cref{def:aas:fork-consistency}).
\end{definition}