In this section, we generalize the notion of an append-only authenticated set from \cref{s:aas} to an \textit{append-only authenticated dictionary} (AAD).
Recall that an AAS stores \textit{elements} and supports (non)membership queries of the form ``Is $e\in S$?''
In contrast, an AAD stores \textit{key-value pairs} and supports \textit{lookups} of the form ``Is $V$ the complete set of values for key $k$?''
In other words, an AAD maps a \textit{key} $k$ to a multiset of \textit{values} $V$ in an append-only fashion.
Specifically, once a value has been added to a key, it cannot be removed nor changed.
For example, if a key is a domain name and its values are certificates for that domain, then an AAD can be used as a Certificate Transparency (CT) log.
In general, keys and values can have any application-specific type.

Naturally, we need new security notions that capture the additional functionality of dictionaries over sets.
Specifically, in an AAS, no malicious server can simultaneously produce accepting proofs of membership and non-membership for the same element $e$ with respect to the same digest.
In contrast, in an AAD, no malicious server can simultaneously produce accepting proofs for two different sets of values $V,V'$ for a key $k$ with respect to the same digest.
This captures the related notion for an AAS since one of the sets of values may be empty (indicating $k$ has never been registered in the dictionary) and the other non-empty.
Similarly, the security definitions for the ``append-only'' property can also be adjusted.