Here, we give detailed algorithms that implement our amortized, dynamic AAS from \cref{s:aas:from-bilinear-acc}.
Recall that our AAS is just a forest of PCTs with corresponding FCTs.
Importantly, recall that our dynamic AAS is a forest that grows over time, as depicted in \cref{f:forest}.
In particular, observe that each forest node has a prefix accumulator associated with it, while root nodes in the forest have FCTs associated with them.
Our algorithms described below operate on this forest, adding new leaves, merging nodes in the forest and computing FCTs in the roots.

An important detail is that a bilinear accumulators $g^{\charpoly_A(s)}$ for a set $A$ is often accompanied by an ``extractable'' counterpart $g^{\tau \charpoly_A(s)}$.
Here $s$ is the $q$-SDH trapdoor and $\tau$ denotes another trapdoor.
The extractable counterpart is necessary to prove security of our (non)membership proofs and our append-only proofs under $q$-PKE (see \cref{s:aas:from-bilinear-acc:proofs}).

\paragraph{Trees Notation.}
\label{s:prelim:notation:trees}
The $|$ symbol denotes string concatenation.
A \textit{tree} is a set of nodes denoted by binary strings in a canonical way.
The root of a tree is denoted by the empty string $\varepsilon$ and the left and right children of a node $w$ are denoted by $w|0$ and $w|1$, respectively.
If $b\in\{0,1\}$, then the sibling of $w = v|b$ is denoted by $\sibling(w) = v|\overline{b}$, where $\overline{b} = 1-b$.
A \emph{path} from one node $v$ to its ancestor node $w$ is denoted by $\treepath[v,w] = \{u_1 = v, u_2 = \parent(u_1), \dots, u_\ell = \parent(u_{\ell-1}) = w\}$.
The parent node of $v = w|b$ is denoted by $\parent(v) = \parent(w|b) = w$.
We also use $\treepath[v,w) = \treepath[v,w]-\{w\}$.

\paragraph{Forest Notation.}
\label{s:prelim:notation:forests}
Let $F_i$ denote a forest of $\le \upperbound$ leaves that only has $i$ leaves in it.
(For example, \cref{f:forest} depicts a forest with $B=8$ growing from one leaf to five leaves.)
Intuitively, a forest is a set of trees where each tree's size is a \textit{unique} power of two (e.g., see $F_5$ in \cref{f:forest}).
The unique tree sizes are maintained by constantly merging trees of the same size.
% When \upperbound = 1, there will be one leaf with 0 bits (\ceil(\log(1)) = 0): the empty string.
% When \upperbound = 2, we need \ceil(\log(2)) = 1 bit for each of the two leaves, and their root will be the empty string, and so on.
% When \upperbound = 3, we need \ceil(\log(3)) = 2 bits for each of the three leaves.
Let $\bin^\upperbound(x)$ denote the $\ceil{\log{\upperbound}}$-bit binary expansion of a number $x$ (e.g., $\bin^{14}(6)=0110$).
(Note that $\bin^1(x) = \varepsilon,\forall x$ because $\ceil{\log{1}}=0$.)
In our AAS, $\bin^\upperbound(i)$ denotes the $i$th inserted leaf, where $i$ starts at 0 (e.g., see leaves 000 through 111 in $F_5$ in \cref{f:forest}).
Let $\roots(F_i)$ denote all the roots of all the trees in the forest (e.g., $\roots(F_5) = \{0, 111\}$ in \cref{f:forest}).
Let $\leaves(F_i)$ denote all the leaves in the forest (e.g., $\leaves(F_3) = \{000, 001, 010\}$ in \cref{f:forest}).

\paragraph{AAS Notation.}
Our algorithms use \textbf{assert} to ensure a condition is true or fail the calling function otherwise. 
Let $\dom(f)$ be the domain of a function $f$. %(i.e. $\forall x \in \dom(f), \exists y$ such that $f(x) = y$).
We use $f(x)=\bot$ to indicate $x\notin \dom(f)$.
Let $\AS_i$ denote our AAS with $i$ elements.
Each node $w$ in the forest stores ``extractable'' accumulators $\acc_w, \eacc_w$ of its PCT together with a Merkle hash $\hash_w$.
Internal nodes (i.e., non-roots) store a subset witness $\subsetProof_w$ between $\acc_w$ and $\acc_{\parent(w)}$.
The digest $d_i$ of $\AS_i$ maps each root $r$ to its Merkle hash $\hash_r$.
Every root $r$ stores a disjointness witness $\disj_r$ between its PCT and FCT.
For simplicity, we assume server algorithms implicitly ``parse out'' the \myblue{\textbf{bolded blue variables}} from $\AS_i$.
% The algorithms below sometimes incrementally build a function $f$ by adding new points $\left(u, v = f(u)\right)$ to its graph, either via $f = f\cup \{(u,v)\}$ or via $f(u) \gets v$.

\paragraph{Server Algorithms.}
{\setup}$(\cdot)$ generates large enough $q$-PKE public parameters $\PPpke_q(g; s,\tau)$ (see \cref{def:q-pke}), given an upper bound $\upperbound$ on the number of elements.
Importantly, the server forgets the trapdoors $s$ and $\tau$ used to generate the public parameters.
In other words, this is a \emph{trusted setup} phase (see \cref{s:prelim:trusted-setup}).

% Assuming elements are hashed to 2\lambda bits:
%
% The size of the AAS server public parameters
% --------------------------------------------
% \upperbound > 0 is the max # of elements
% When \upperbound = 2^k:
%  - the worst-case forest has a single PCT with \upperbound leaves, one for each element
%  - each element has 2\lambda bits and thus 2\lambda + 1 prefixes (b.c. we include the empty prefix \varepsilon, which we could exclude actually, since all elements have it)
%  - so, the root node of the PCT accumulates (2\lambda + 1)\upperbound prefixes (this is only true for \upperbound = 1 because, when \upperbound > 1, some prefixes will coincide)
% When 2^k < \upperbound < 2^{k+1}:
%  - the worst-case forest's largest PCT has \ell = 2^{\floor{\log{\upperbound}}} leaves
%    (e.g., If \upperbound = 10, the largest PCT will have 8 leaves, and the next PCT will have 2 leaves.
%     Incidentally, when \upperbound is not a power of two, we actually support adding more than \upperbound elements: 2^{k+1} - 1 to be exact.
%     For \upperbound = 10, we can add 8 + 4 + 2 + 1 = 15.)
%  - so, the root node of the PCT accumulates (2\lambda+1)\ell prefixes
%
% So, in general, we need (2\lambda+1)\ell prefixes in the root node of the largest PCT, where \ell = 2^{\floor{\log{\upperbound}}}
% Since a polynomial $\sum_{i=1}^q (x-r_i)$ with $q$ roots has degree $q$, that means the degree of the root prefix accumulator will be (2\lambda+1)\ell.
% (Note: In the implementation, we could avoid accumulating the empty prefix, since all keys will have it. But we do not.)
%
% The size of the AAS clients public parameters
% ---------------------------------------------
% The client needs to be able to reconstruct any leaf accumulato over 2\lambda+1 prefixes.
% So he needs to commit to polynomials of degree exactly $q=2\lambda + 1$

\begin{algorithm}[H]
    %\footnotesize
    %\small
    \begin{algorithmic}[1]
    \caption{\small Computes public parameters (trusted setup)}
    \label{a:aas:setup}
    \Function{\setup}{$1^\lambda, \upperbound$} $\rightarrow (\pp, \vk)$ \Comment{Generates $q$-PKE public parameters}
        \State
            $\ell \gets 2^{\floor{\log{\upperbound}}} \qquad
             q \gets (2\lambda + 1)\ell \qquad
             ( \Group,\GT,p,g,e(\cdot,\cdot) ) \leftarrow \groupkosetup(1^\lambda)$
        \State
            $s\stackrel{\$}{\gets} \Fp \qquad
             \tau\stackrel{\$}{\gets} \Fp \qquad
             \vk=((g^{s^i})_{i=0}^{2\lambda + 1}, g^\tau)$
        \State \Return $((( \Group,\GT,p,g,e(\cdot,\cdot) ), \upperbound, \PPpke_q(g; s,\tau)), \vk )$
    \EndFunction
    \end{algorithmic}
\end{algorithm}

\begin{algorithm}[H]%[tb] % sigle column
    \caption{\small Appends a new $i$th element to the AAS, $i\in[0,\upperbound-1]$}
    \label{a:aas:append}
    %\footnotesize
    %\small
    \begin{algorithmic}[1]
    \Function{\append}{$\pp,\AS_i, d_i, k$} $\rightarrow (\AS_{i+1}, d_{i+1})$
        \State $w \gets \bin^\upperbound(i) \qquad \elems_w \gets \{k\}$\Comment{Create new leaf $w$ for element $k$}
        \label{a:aas:append:create-leaf-begin}
        \State $(\accpoly_w, {\acc}_w, \cdot) \gets \accumulate(\prefixes(\elems_w)) \quad \hash_w \gets \Hb(w|\bot|{\acc}_w|\bot)$
        \label{a:aas:append:create-leaf-end}

        \LineComment{``Merge'' old PCT roots with new PCT root (recursively)}
        \While{$\sibling(w)\in \roots(F_i)$}
        \label{a:aas:append:merge-begin}
            \State $\ell \gets\sibling(w) \qquad p\gets \parent(w) \qquad \elems_p \gets \elems_\ell\cup \elems_w$
            \State $(\accpoly_p, {\acc}_p, \eacc_p) \gets \accumulate(\prefixes(\elems_p))\qquad \hash_p = \Hb(p|\hash_\ell|{\acc}_p|\hash_w)$
            \State $(\cdot, \subsetProof_\ell, \cdot) \gets \accumulate(\prefixes(\elems_p\setminus \elems_\ell))$
            \State $(\cdot, \subsetProof_w, \cdot) \gets \accumulate(\prefixes(\elems_p \setminus \elems_w)) \qquad w\gets p$
        \EndWhile
        \label{a:aas:append:merge-end}
        % Note: Adding a single leaf will always create exactly one new root, possibly by merging more than two old roots.

        \LineComment{Invariant: $w$ is a new root in $F_{i+1}$. Next, computes $w$'s frontier.}
        \label{a:aas:append:root-at-begin}
        \State $(\fropoly_w,\bft_w) \gets \createfrontier(F(\elems_w))$
        % We need frontier polynomial \fropoly_w here to compute the EEA coeffs below!
        \State $(y,z)\gets \mathsf{ExtEuclideanAlg}(\accpoly_w, \fropoly_w)\qquad {\disj}_w \gets ( g^{y(s)}, g^{z(s)})$
        \label{a:aas:append:root-at-end}

        \State Store updated AAS state (i.e., the \myblue{\textbf{bolded blue}} variables) into $\AS_{i+1}$
        \State $d_{i+1}(r) \gets \hash_r, \forall r \in \roots(F_{i+1})$\Comment{Set new digest}
        \State \Return $\AS_{i+1}, d_{i+1}$
    \EndFunction

    % Note that this function is implicitly given access to all the public parameters it needs.
    \Function{\accumulate}{$T$}
        \State \Return $(\accpoly, g^{\accpoly(s)}, g^{\tau \accpoly(s)})$ where $\accpoly(x)=\prod_{w \in T} {(x-\Hp(w))}$
    \EndFunction
    \end{algorithmic}
\end{algorithm}

{\append}$(\cdot)$ creates a new leaf $\ell$ for the element $k$ (\crefrange{a:aas:append:create-leaf-begin}{a:aas:append:create-leaf-end}).
It recursively merges equal-sized PCTs in the forest, as described in \cref{s:aas:from-bilinear-acc} (\crefrange{a:aas:append:merge-begin}{a:aas:append:merge-end}).
In this process, it computes subset witnesses between old PCT roots and the new PCT.
Merging ends when the newly created PCT $w$ has no equal-sized PCT to be merged with.
Recall from \cref{s:prelim:polycommit} that $\Hp$ maps elements to be accumulated to field elements in $\Fp$.

If $k$ is in the set, $\provememb(\cdot)$ sends a Merkle path to $k$'s leaf in some tree with root $r$ (\crefrange{a:aas:provememb:paths-begin}{a:aas:provememb:paths-end}) via $\provepath(\cdot)$ (see \cref{a:aas:provepath}).
This path contains subset witnesses between every node's accumulator and its parent node's accumulator.
If $k$ is not in the set, then $\provememb(\cdot)$ sends frontier proofs in each FCT in the forest (\crefrange{a:aas:provememb:frontier-begin}{a:aas:provememb:frontier-end}) via $\provefrontier(\cdot)$ (see \cref{a:at:provefrontier}).

\begin{algorithm}[H]%[tb] % sigle column
    \caption{\small Constructs a (non)membership proof}
    \label{a:aas:provememb}
    \label{a:aas:provepath}
    %\footnotesize
    \begin{algorithmic}[1]
    \Function{\provememb}{$\pp,\AS_i,k$} $\rightarrow (b,\pi)$
        \State Let $\ell\in \leaves(F_i)$ be the leaf where $k$ is stored or $\bot$ if $k\notin \AS_i$
        \If{$k \in \AS_i$} \Comment{Construct Merkle path to element}
            \label{a:aas:provememb:paths-begin}
            \State Let $r\in \roots(F_i)$ be the root of the tree where $k$ is stored
            \State $\pi \gets \provepath(\AS_i, \ell, r,\bot)\qquad b\gets 1$ % \qquad R\gets R-\{r\}
            \label{a:aas:provememb:paths-end}
        \Else \Comment{Prove non-membership in all FCTs}
            \label{a:aas:provememb:frontier-begin}
            \State $\CP_r\gets \provefrontier(\AS_i,r,k),\forall r\in \roots(F_i)$
            % We don't need extractability for prefix accumulators in non-membership proofs
            % We do need the hashes of the root's children (if any) for the client to verify this prefix accumulator against the Merke root hash
            % (note if r|c does not exist because r is a leaf, then we assume h_{r|c} equals \bot)
            \State $\pi\gets \proverootaccs(\AS_i, \pi)\quad b\gets 0$
            \label{a:aas:provememb:frontier-end}
        \EndIf
        \State \Return $b, ( \ell, \pi, (\CP_r)_{r\in \roots(F_i)}, (\disj_r)_{r\in \roots(F_i)})$
    \EndFunction

    % Includes leaf (u) and root (r) prefix accumulators, as well as (u)'s subset witness
    \Function{\provepath}{$\AS_i,u,r,\pi$} $\rightarrow \pi$\Comment{Precondition: $r$ is a root in $F_i$}
        \State $\pi(r) \gets ( \bot, \acc_r, \eacc_r, \bot)$
        \LineComment{Overwrites $\pi(w)$ set by previous \provepath call (if any)}
        \State $\pi(w) \gets ( \bot, \acc_w, \eacc_w, \subsetProof_w), \forall w\in \treepath[u,r)$
        \LineComment{Only sets $\pi(\sibling(w))$ if not already set from previous \provepath call!}
        \For{$w\in \treepath[u,r)$ where $\sibling(w)\notin \dom(\pi)$}
            \State $\pi(\sibling(w)) \gets ( \hash_{\sibling(w)}, \bot,\bot,\bot)$
        \EndFor
        \State \Return $\pi$
    \EndFunction

    \Function{\proverootaccs}{$\AS_i,\pi$} $\rightarrow \pi$
        % Note: Non-membership proofs don't need the extractable counterpart, but \verappendonly does.
        \State $\pi(r)\gets (\bot,\acc_{r}, \eacc_{r}, \bot), \forall r\in\roots(F_i),$
        \State $\pi(r|c)\gets (\hash_{r|c},\bot,\bot,\bot), \forall r\in\roots(F_i), \forall c\in \{0,1\}$
    \EndFunction
    \end{algorithmic}
\end{algorithm}

For each root $r$ in $F_i$, {\proveappendonly}$(\cdot)$ sends a Merkle path to an ancestor root in $F_j$, if any.
The Merkle path contains subset witnesses between all prefix accumulators along the path.
It also contains the root prefix accumulators from $F_i$, which the client will verify against his digest $d_i$.

\paragraph{Client Algorithms.}
{\verappendonly}$(\cdot)$ first ensures that $d_i$ and $d_j$ are digests at version $i$ and $j$, respectively (\crefrange{a:aas:verappendonly:check-digest-begin}{a:aas:verappendonly:check-digest-end}).
This involves checking that $d_i$ has the expected number of roots (i.e., same as in $F_i$) and that the Merkle hash of each root $r$ in $d_i$ is computed with the correct label $r$ as $d_i(r)=\Hb(r|h_{r|0}|a_r|h_{r|1})$.
However, for simplicity of exposition, \crefrange{a:aas:verappendonly:check-digest-begin}{a:aas:verappendonly:check-digest-end} of {\verappendonly}$(\cdot)$ leave these details out.

Before checking subset witnesses, {\verappendonly}$(\cdot)$ validates the old root prefix accumulators in $\pi_{i,j}$ against the Merkle roots in $d_i$ (\crefrange{a:aas:verappendonly:check-old-root-accs-begin}{a:aas:verappendonly:check-old-root-accs-end}).
Without this check, any old root prefix accumulator could be maliciously given in the append-only proof $\pi_{i,j}$, breaking the append-only property.
Then, it checks that each root $r$ from $F_i$ is a subset of some root in $F_j$ by checking subset witnesses (\cref{a:aas:verappendonly:paths}) via $\verpath(\cdot)$ (see \cref{a:helper:verpath}).

{\verappendonly}$(\cdot)$ enforces fork consistency implicitly when verifying Merkle hashes.
For this to work, \cref{a:aas:verappendonly:well-formed} first ensures that the Merkle paths from the old roots to the new roots are ``well-formed.''
This means checking that the proof paths contains all the expected sibiling Merkle hashes, at the right positions, and no other Merkle hashes.
If other Merkle hashes were included, our recursive $\mathsf{MerkleHash}(\cdot)$ implementation could be tricked into thinking an invalid Merkle path validates.

\begin{algorithm}[H]%[tb] % sigle column
    \caption{\small Creates and verifies append-only proofs}
    \label{a:aas:proveappendonly}
    \label{a:aas:verappendonly}
    %\footnotesize
    \begin{algorithmic}[1]
    \Function{\proveappendonly}{$\pp,\AS_i,\AS_j$} $\rightarrow \pi$
        \If{$\roots(F_i)\subset\roots(F_j)$}
            \Return $\bot$
        \EndIf
        \State Let $R=\{$roots $\in F_i$ but $\not\in F_j\}$ and $r'\in \roots(F_j)$ be their ancestor root
        % Note: When adding two paths, appends to proof \pi or even overwrites it
        \State $\pi\gets \provepath(\AS_j, r,r',\pi), \forall r \in R\quad \pi\gets\proverootaccs(\AS_i,\pi)$
        \State \Return $\pi$
    \EndFunction

    \Function{\verappendonly}{$\vk, d_i, i, d_j, j, \pi_{i,j}$} $\rightarrow \{T,F\}$
        % Version of digest is implicitly given by the node numbering fixed through Merkle hashing
        % For the fork consistency definition, VerAppendOnly needs to check the old version of the digest too (technicality).
        \Assert $d_i(r) \ne \bot \Leftrightarrow r\in \roots(F_i)$ \Comment{Is valid version $i$ digest?}
        \label{a:aas:verappendonly:check-digest-begin}
        \Assert $d_j(r) \ne \bot \Leftrightarrow r\in \roots(F_j)$ \Comment{Is valid version $j$ digest?}
        \label{a:aas:verappendonly:check-digest-end}
        \Assert $\forall r \in \roots(F_i) \cap \roots(F_j), d_i(r)=d_j(r)$
        
        \State Let $R=\{$roots $\in F_i$ but $\not\in F_j\}$ \Comment{i.e., old roots with paths to new root}
        % Recall that d_i(r) only stores the Merkle root hash h_r and not the prefix accumulator a_r.
        % The proof \pi_{i,j} will give a_r but it could give a completely different one, breaking the append-only property.
        % Thus, whatever it gives must be verified.
        \ForAll{$r\in \roots(F_i)$} \Comment{Check proof gives correct old root accumulators}
            \label{a:aas:verappendonly:check-old-root-accs-begin}
            \State $(\cdot,a_{r},\cdot,\cdot)\gets \pi(r)$ \quad $({h}_{r|b},\cdot,\cdot,\cdot) \gets \pi(r|b),\forall b\in \{0,1\}$
            \Assert $d_i(r) = \Hb(r|h_{r|0}|a_r|h_{r|1})$
        \EndFor
        \label{a:aas:verappendonly:check-old-root-accs-end}
        \State $\forall r\in R$, fetch $h_r$ from $d_i(r)$ and update $\pi_{i,j}(r)$ with it
        \Assert $\pi_{i,j}$ is well-formed Merkle proof for all roots in $R$
        \label{a:aas:verappendonly:well-formed}
        \Assert $\forall r\in R,\verpath(d_j, r, \pi_{i,j})$
        \label{a:aas:verappendonly:paths}
    \EndFunction
    \end{algorithmic}
\end{algorithm}

If $k$ is stored at leaf $\ell$ in the AAS, {\vermemb}$(\cdot)$ reconstructs $\ell$'s accumulator from $k$.
Then, it checks if there's a valid Merkle path from $\ell$ to some root, verifying subset witnesses along the path via $\verpath(\cdot)$ (see \cref{a:helper:verpath}).
If $k$ is not in the AAS, {\vermemb}$(\cdot)$ verifies frontier proofs for $k$ in each FCT in the forest via $\verfrontier(\cdot)$ (see \cref{a:at:verfrontier}).

\begin{algorithm}[H]%[tb] % single column
    \caption{\small Verifies a (non)membership proof}
    \label{a:aas:vermemb}
    \label{a:helper:verpath}
    %\footnotesize
    \begin{algorithmic}[1]
    \Function{\vermemb}{$\vk, d_i,k,b,\pi_k$} $\rightarrow \{T,F\}$
    \State Parse $\pi_{k}$ as $\ell, \pi, (\CP_r)_{r\in \roots(F_i)}, (y_r, z_r)_{r\in \roots(F_i)}$
    \If{$b = 1$} \Comment{This is a membership proof being verified}
    \label{a:aas:vermemb:foreach-leaf}
        \label{a:aas:vermemb:verpath-begin}
        \State $(\cdot, a_\ell, \hat{a}_\ell)\gets \accumulate(\prefixes(\{k\}))\qquad h_\ell \gets \Hb(\ell|\bot|a_\ell|\bot)$
        % VerPath will need a_\ell when recursively checking the append-only property
        % Also, this is an update, not an overwrite, because we have to preserve the subset witness from \pi(\ell) (if any)
        \State Update $\pi(\ell)$ with $h_\ell$ and accumulators $a_\ell$ and $\hat{a}_\ell$
        \Assert $\pi$ is well-formed Merkle proof for leaf $\ell \wedge {\verpath(d_i, \ell, \pi)}$
        \label{a:aas:vermemb:verpath-end}
    \Else  \Comment{This is a non-membership proof being verified}
        \label{a:aas:vermemb:verfrontier-begin}
        % Get FCT and PCT accs. Validate PCT accs against digest.
        \ForAll{$r\in \roots(F_i)$} \Comment{Check FCTs}
            \State $(\cdot,a_{r},\cdot,\cdot)\gets \pi(r)$ \quad $(o_r, \cdot) \gets \CP_r(\varepsilon)$
            \State $({h}_{r|b},\cdot,\cdot,\cdot) \gets \pi(r|b),\forall b\in \{0,1\}$
            \Assert $d_i(r) = \Hb(r|h_{r|0}|a_r|h_{r|1})$
            \Assert $e(a_r,y_r)e(o_r,z_r) = e(g,g) \wedge \verfrontier(k, \CP_r)$
        \EndFor
        \label{a:aas:vermemb:verfrontier-end}
    \EndIf
    \EndFunction

    % Note: w is always a node in F_i
    \Function{\verpath}{$d_k,w,\pi$} $\rightarrow \{T,F\}$ \Comment{Checks Merkle path from $w$ to some root in $d_k$}
        \State Let $r\in \roots(F_k)$ denote the ancestor root of $w$
        \LineComment{Walk path invariant: $u$ is \textit{not} a root node (but $\parent(u)$ might be)}
        \For{$u\gets w; u \neq r; u\gets\parent(u)$}
            \State $p \gets \parent(u)$\Comment{Check subset witness and extractability (below)}
            \State $(\cdot, a_{u}, \hat{a}_{u}, \pi_{u}) \gets \pi(u)\quad(\cdot, a_{p}, \hat{a}_{p}, \cdot) \gets \pi(p)$
            \Assert $e(a_u, \pi_u) = e(a_p, g) \wedge e(a_u, g^\tau) = e(\hat{a}_u, g)$
            \label{a:aas:verpath:extractability-check}
        \EndFor
        \Assert $d_k(r) = \mathsf{MerkleHash}(\pi, r)$ \Comment{Invariant: $u$ equals $r$ now}
        \label{a:aas:verpath:merklehash}
        \Assert $e(a_r, g^\tau) = e(\hat{a}_r, g)$\Comment{Is root accumulator extractable?}

    \EndFunction
    % Note: Does NOT modify Merkle proof \pi. Just returns the computed Merkle root hash.
    \Function{$\mathsf{MerkleHash}$}{$\pi, w$} $\rightarrow h_w$
    \label{a:aas:merklehash}
        \State $(h_w, a_w, \cdot,\cdot) \gets \pi(w)$
        \If{$h_w = \bot$}
            \State \Return $\Hb(w|\mathsf{MerkleHash}(\pi, w|0)|a_w|\mathsf{MerkleHash}(\pi, w|1))$
        \Else
            \State \Return $h_w$
        \EndIf
    \EndFunction
    \end{algorithmic}
\end{algorithm}

\paragraph{Frontier Algorithms.}
{\createfrontier}$(\cdot)$ creates a FCT level by level, starting from the leaves, given a set of frontier prefixes $F$.
Given a key $k\notin \AS_i$ and a root $r$, {\provefrontier}$(\cdot)$ returns a frontier proof for $k$ in the FCT at root $r$.
{\verfrontier}$(\cdot)$ verifies a frontier proof for one of $k$'s prefixes against a specific root FCT accumulator.
\begin{algorithm}[H]
    \begin{algorithmic}[1]
    \caption{\small Manages FCT of a set}
    \label{a:at:createfrontier}
    \label{a:at:provefrontier}
    \label{a:at:verfrontier}
    %\footnotesize
    \Function{\createfrontier}{$F$} $\rightarrow (\phi,\sigma)$
        \State $i\gets 0\qquad S_w\gets \varnothing, \forall w$
        \For{$\rho \in F$} \Comment{First, build FCT leaves, with $g^{s-\Hp(\rho)}$ for each prefix $\rho$}
            \State $w\gets \bin^{|F|}(i)\qquad S_w \gets \rho\qquad i\gets i+1$
            \State $(\fropoly_w,\fac,\efac) \gets \accumulate(S_w)\quad \sigma(w) \gets (\fac, \efac)$
        \EndFor

        % Example: When |F| = 5, this code merges the first two leaves, then the next two leaves, then for the 5th leaf without a sibling, it just "merges" it with its empty sibling.
        % In other words, its parent will have the same frontier accumulator and the tree looks like this:
        %        r
        %    -       -
        %  *   *   *
        % 1 2 3 4 5
        % In our C++ implementation, we have a more efficient implementation, where the tree looks like this:
        %        r
        %    -       5
        %  *   *
        % 1 2 3 4
        \For{$i \gets \ceil{\log{|F|}}; i\ne 0; i\gets i-1$} \Comment{Then, build FCT level by level}
            \State $j\gets 0\qquad \mathsf{levelSize} \gets 2^i\qquad u\gets \bin^{\mathsf{levelSize}}(0)$
            \While{$S_u \ne \varnothing$} \Comment{Merge sibling accumulators on level $i$}
                \State $p \gets \parent(u)\quad S_p \gets S_u\cup S_{\sibling(u)} \quad j \gets j+2$
                \State $(\fropoly_p,\fac,\efac) \gets \accumulate(S_p)\quad \sigma(p) \gets (\fac, \efac)\quad u \gets \bin^\mathsf{levelSize}(j)$
            \EndWhile
        \EndFor
        \State \Return $( \fropoly_\varepsilon, \sigma)$
    \EndFunction

    \Function{\provefrontier}{$\AS_i, r, k$} $\rightarrow \CP$
        \State Let $\rho$ be the smallest prefix of $k$ that is not in $\prefixes(\elems_r)$
        \State Let $\ell$ denote the leaf where $\bft_r(\ell) = g^{(s-\Hp(\rho))}$
        \State $\CP(\varepsilon) \gets \bft_r(\varepsilon)$ \Comment{Copy root FCT accumulator}
        \For{$w\in \treepath[\ell, \varepsilon)$}\Comment{Copy path to $\rho$'s FCT leaf}
            \State $\CP(w) \gets \bft_r(w)$
            \If{$\bft_r(\sibling(w))\ne \bot}$
                % Note: Siblings need not be extractable, but for simplicity of the code we don't optimize.
                % Asymptotically, proof-size remains the same.
                \State $\CP(\sibling(w)) \gets \bft_r(\sibling(w))$
            \Else
                % This handles frontier tree sizes that are not powers of two.
                % Continuing with the |F|=5 example from \createfrontier, the 5th leaf (at level 3) would have an empty sibling.
                % So would its parent at level 2. But its parent at level 1 wouldn't. And level 0 is the root. Just look at the tree:
                %
                %        r
                %    -       -
                %  *   *   *
                % 1 2 3 4 5
                \State $\CP(\sibling(w)) \gets (g, g^\tau)$
            \EndIf
        \EndFor
        \State \Return $\CP$
    \EndFunction

    \Function{\verfrontier}{$k,\CP$} $\rightarrow \{T,F\}$
        \LineComment{Find leaf $\ell$ in $\CP$ with a prefix $\rho$ for $k$, or fail.}
        \Assert $\exists \ell,\rho$ such that $\rho\in \prefixes(\{k\}) \wedge g^{(s-\Hp(\rho))} = \CP(\ell)$
        \Assert $e(\fac, g^\tau) = e(\efac_w, g)$ where $(\fac,\efac)\gets \CP(\varepsilon)$
        %\Comment{Root FCT accumulator is extractable?}
        % NOTE: The 'for' loop below implicitly verifies against root in FCT as well!
        \For{$w\in \treepath[\ell, \varepsilon)$}\Comment{Verify $\rho$'s membership in the FCT}
            \State $(c_w,\hat{c}_w) \gets \CP(w)\quad (s_w,\cdot)\gets \CP(\sibling(w))$
            \State $(p_w,\cdot) \gets \CP(\parent(w))$
            \Assert $e(c_w, s_w) = e(p_w, g)\wedge e(c_w, g^\tau) = e(\hat{c}_w, g)$
        \EndFor
    \EndFunction
    \end{algorithmic}
\end{algorithm}
