Membership and append-only correctness follow from close inspection of the algorithms. 
Here, we prove our AAS construction offers membership and append-only security, as well as fork consistency.

\subsubsection{Membership Security}
\label{s:aas:from-bilinear-acc:proofs:membership-security}
Assume there exists a polynomial-time adversary \Adv that produces digest $d$, element $k$ and inconsistent proofs $\pi,\pi'$ such that $\vermemb(VK,d,k,1,\pi)$ and $\vermemb(VK,d,k,0,\pi')$ both accept. 
We describe how \Adv can either find a collision in $\Hb$ (used to hash the PCTs) or break the $q$-SBDH assumption.

\begingroup
\renewcommand{\myblue}[1]{\textcolor{black}{#1}}
\renewcommand{\mathbf}[1]{#1}
\renewcommand{\boldsymbol}[1]{#1}

First, let us focus on the membership proof $\pi$, which consists of a path to $k$'s leaf in some PCT of size $2^\ell$ leaves.
% Q: If the verifier computes the leaf prefix accumulator, what is the length of this path in a tree of $2^\ell$ leaves?
% For example, say tree is of size 2^2 = 4, so it has 3 levels of nodes (i.e., 4 leaves + another 2 nodes at the next level + 1 root).
% Then, the proof will send accumulators at the root level and the one below it + 2 subset witnesses (between leaf and its parent and between root and its child)
Let $\acc_0,\acc_1,\dots,\acc_{\ell}$ be the prefix accumulators along this path (part of $\pi$), where $\acc_0$ is the leaf accumulator for element $k$ with characteristic polynomial $A_0(x) = \prod_{c \in \prefixes(k)}(x-\Hp(c))$.
% Note that $a_\ell$ is the root prefix accumulator.
Let $\pi_0, \dots, \pi_{\ell-1}$ denote the corresponding subset witnesses, such that $e(\acc_j, g) = e(\acc_{j-1}, \pi_{j-1}), \forall j \in [\ell]$.

Second, let us consider the other (contradictory) non-membership proof $\pi'$, which consists of a path to a FCT leaf storing a prefix $\rho$ of $k$.
Let $\fac_0, \fac_1,\dots,\fac_{\ell'}$ be the frontier accumulators along this path, where $\fac_0$ is the leaf accumulator for $\rho$ with characteristic polynomial $O_0(x) = x-\Hp(\rho)$.
Note that this FCT is of size $2^{\ell'}$, which might differ from $2^\ell$, the size of $\pi$'s PCT.
Let $\acc^*_\ell$ be the root prefix accumulator for this FCT's corresponding PCT, as contained in $\pi'$ (see \cref{a:aas:provememb}).

When verifying $\pi$ and $\pi'$, both $\acc_\ell$ and $\acc^*_\ell$ are hashed (together with the two claimed hash values of their children) and the result is checked against the hash from digest $d$.
Since verification of $\pi$ and $\pi'$ succeeds, if $\acc_\ell \neq \acc^*_\ell$ this would produce a collision in $\Hb$.

Else, we argue as follows.
Each prefix accumulator $\acc_1,\dots,\acc_\ell$ is accompanied by an extractability term $\eacc_1,\dots,\eacc_\ell$, which the client checks as $e(\acc_j,g^\tau)= e(\eacc_j,g)$ for $j\in[\ell]$ (see \cref{a:aas:verpath:extractability-check} in \cref{a:helper:verpath}).
Hence, from the $q$-PKE assumption, it follows that there exists a polynomial-time algorithm that, upon receiving the same input as \Adv, outputs polynomials $(A_j(x))_{j\in[\ell]}$ (in coefficient form) such that $g^{A_j(s)} = \acc_j$ with all but negligible probability.
The same holds for all frontier accumulators $\fac_1,\dots,\fac_{\ell'}$ and terms $\efac_1,\dots,\efac_{\ell'}$ included in $\pi'$, and let $(O_{j}(x))_{j\in[\ell']}$ denote their polynomials.

% The key idea is that just because the accumulators pass the subset tests, it doesn't necesarily mean the extracted polynomials will also pass.
We distinguish two cases and analyze them separately:
\begin{itemize}
    \item[(a)] $ (x-\Hp(\rho)) \nmid A_\ell(x)$ or $ (x-\Hp(\rho)) \nmid O_{\ell'}(x)$
    \item[(b)] $ (x-\Hp(\rho)) \;|\; A_\ell(x)$ and $ (x-\Hp(\rho)) \;|\; O_{\ell'}(x)$
\end{itemize}

For case (a), without loss of generality we will focus on the $(x-\Hp(\rho)) \nmid A_\ell(x)$ sub-case.
(The proof for the second sub-case proceeds identically.)
% Important: This is when frontier accumulators must be extractable.
% See how we treat first sub-case below.
% The second sub-case would be the same except it would need to extract frontier polynomials].
Observe that, by construction, $(x-\Hp(\rho)) \mathrel| A_0(x)$ and, by assumption, $(x-\Hp(\rho)) \nmid A_\ell(x)$.
Thus, there must exist some index $0 < i \le \ell$ such that $(x-\Hp(\rho)) \mathrel| A_{i-1}(x)$ and $(x-\Hp(\rho)) \nmid A_i(x)$.
% Why must there exist such an i?
% We have a sequence of polynomilas A_0, A_1, \dots, A_\ell, where the first is divisible and the last isn't. 
% There has to be an index where the polynomials "stop being divisible."
% In the worst-case, they are divisible until A_\ell, in which case i = \ell.
% In the best-case, they are only divisible at A_0, in which case i = 1.
Note that $i$ can be easily deduced given all  $(A_j(x))_{j\in[\ell]}$.
% Note that when $i = 1$, $(x-\Hp(\rho))$ always divides $A_0$ which is the characteristic polynomial of $k$'s prefixes.
Therefore, by polynomial division there exist efficiently computable polynomials $q_{i}{(x)},q_{i-1}(x)$ and $\kappa\in \Fp$ such that: $A_{i-1}(x) = (x-\Hp(\rho))\cdot q_{i-1}(x)$ and $A_{i}(x) = (x-\Hp(\rho))\cdot q_{i}(x) + \kappa$.

Now, during the verification of the $i$th subset witness, it holds that:
\begin{align*}
    e(\acc_i,g) &= e(\acc_{i-1},\pi_{i-1}) \Leftrightarrow\\
    e(g^{A_i(s)},g) &= e(g^{A_{i-1}(s)},\pi_{i-1})\Leftrightarrow\\
    e(g^{(s-\Hp(\rho))\cdot q_{i}(s) + \kappa},g) &= e(g^{(s-\Hp(\rho))\cdot q_{i-1}(s)},\pi_{i-1})\Leftrightarrow\\
        e(g^{q_{i}(s) + \frac{\kappa}{(s-\Hp(\rho))}},g) &= e(g^{q_{i-1}(s)},\pi_{i-1})\Leftrightarrow\\
        e(g^{\frac{\kappa}{(s-\Hp(\rho))}},g) &= e(g^{q_{i-1}(s)},\pi_{i-1})\cdot e(g^{-q_{i}(s)},g)\Leftrightarrow\\
        e(g^{\frac{1}{(s-\Hp(\rho))}},g) &= \left[ e(g^{q_{i-1}(s)},\pi_{i-1})\cdot e(g^{-q_{i}(s)},g)\right]^{\kappa^{-1}}.
\end{align*}
Hence, the pair $(\Hp(\rho), \left[ e(g^{q_{i-1}(s)},\pi_{i-1})\cdot e(g^{-q_{i}(s)},g)\right]^{\kappa^{-1}})$ can be used to break the $q$-SBDH assumption.

In case (b), by assumption, $(x-\Hp(\rho)) \mathrel| A_\ell(x)$ and $ (x-\Hp(\rho)) \mathrel| O_{\ell'}(x)$. 
Therefore, by polynomial division there exist efficiently computable polynomials $q_A{(x)},q_o(x)$ such that: 
$A_{\ell}(x) = (x-\Hp(\rho))\cdot q_A(x)$ and $O_{\ell'}(x) = (x-\Hp(\rho))\cdot q_o(x)$.
Let $\disj = (y,z)$ be the disjointness witness from $\pi'$.
Since $\disj$ verifies against accumulators $\acc_\ell$ and $\fac_{\ell'}$, it holds that:
\begin{align*}
    e(\acc_\ell,y) \cdot e(\fac_{\ell'},z) &= e(g,g) \Leftrightarrow\\
    e(g^{A_\ell(s)},y) \cdot e(g^{O_{\ell'}(s)},z) &= e(g,g) \Leftrightarrow\\
    e(g^{(s-\Hp(\rho))\cdot q_A(s)},y) \cdot     e(g^{(s-\Hp(\rho))\cdot q_o(s)},z) &= e(g,g)\Leftrightarrow\\
    e(g^{q_A(s)},y) \cdot e(g^{q_o(s)},z) &= e(g,g)^{\frac{1}{(s-\Hp(\rho))}}.
\end{align*}
Thus, the pair $(\Hp(\rho), e(g^{q_A(s)},y) \cdot e(g^{q_o(s)},z))$ can again be used to break the $q$-SBDH assumption.

\subsubsection{Append-only Security}
\label{s:aas:from-bilinear-acc:proofs:append-only-security}
We can prove append-only security with the same techniques used above. 
Let $\rho$ be the prefix of $k$ used to prove non-membership w.r.t. the new digest $d_{j}$.
The membership proof for $k$ w.r.t. the old digest $d_i$ again involves a series of prefix accumulators whose corresponding polynomials can be extracted.
By our previous analysis, $(x-\Hp(\rho))$ must divide the polynomial extracted for the root prefix accumulator in $d_i$, otherwise the $q$-SBDH assumption can be broken.
% In other words, this is case (a) of our membership security proof where we only use the prefix accumulators/polynomials to break $q$-SBDH
Continuing on this sequence of subset witnesses, the append-only proof ``connects'' this old root prefix accumulator to a new root prefix accumulator in $d_{j}$.
By the same argument, $(x-\Hp(\rho))$ must also divide the polynomial extracted for this new root prefix accumulator from $d_j$.
Since non-membership also verifies, $(x-\Hp(\rho))$ must divide the extracted polynomial for the root frontier accumulator in $d_{j}$, or else $q$-SBDH can be broken.
Finally, we apply the same argument as case (b) above, since $(x-\Hp(\rho))$ divides both these polynomials and we have a disjointness witness for their accumulators, again breaking $q$-SBDH.

\subsubsection{Fork Consistency}
\label{s:aas:from-bilinear-acc:proofs:fork-consistency}
Assume there exists a polynomial-time adversary \Adv that breaks fork consistency, producing digests $d_i\ne d'_i$ with append-only proofs $\pi_i,\pi'_i$ to a new digest $d_j$.
Since $d_i\ne d'_i$, there exists a root $r$ such that its hash $h_r$ in $d_i$ differs from its hash $h'_r$ in $d'_i$. % e.g., r = 00 in \cref{f:forest}
Since $d_i$ and $d'_i$ get ``joined'' into $d_j$, let $r^*\neq r$ denote the ancestor root of $r$ in $d_j$.
% e.g., r' = 0 \in cref{f:forest}
(Note that $r^* \neq r$, since \verappendonly always makes sure that common roots between an old digest and a new digest have the same hash.) 
% e.g., if proving F_2 and F_3 are append-only, then root 00 is 'common' between the two forests, and \verappendonly will ensure h_{00} remains the same in d_3. 
% Therefore, we need only consider strict ancestors r^* of r.
Now, note that both proofs $\pi_i,\pi'_i$ are Merkle proofs from node $r$ to $r^*$.
Importantly, because every node $w$ is hashed together with its label $w$ (as $h_w = \Hb(w,h_{w|0},a_w,h_{w|1})$), the two Merkle proofs take the same path (i.e., $\treepath[r,r^*]$)!
In other words, the adversary produced two Merkle proofs that (1) verify against the same digest $d_j$, (2) take the same path to the same leaf $r$, but (3) attest for different leaf hashes $h_r$ and $h_r'$.
This breaks Merkle hash tree security and can be used to produce a collision in $\Hb$.

\endgroup