This thesis makes progress on two fundamental problems in cryptography: keeping secrets and exchanging public keys.

First, we showed how to scale verifiable secret sharing (VSS) to millions of participants.
Our scalable VSS protocol can be used to make leaking a secret key much harder by splitting it across millions of devices and forcing adversaries to compromise more than half of them.
We then showed how to use such a secret to \textit{quickly} sign messages only if more than half of the million signers cooperate.
Specifically, we proposed a threshold signature scheme (TSS) that scales to millions of signers.
Compared to previous TSSs at this scale, our scheme can sign a message in tens of seconds rather than tens of hours.
Our TSS can be used to decentralize signing authorities on the Internet and to create randomness beacons.
Yet to securely bootstrap our scalable TSS, we need a scalable distributed key generation (DKG) to securely generate its key without anybody learning it.
For this, we showed how to use our scalable VSS to obtain a scalable DKG.
At the same time, we left some problems to future work, such as the VSS/DKG broadcast channel and the worst-case overhead of complaints in DKGs.

Second, we showed how to build append-only logs using only a single untrusted server and no additional trust assumptions.
Our construction is the first to achieve logarithmic proof sizes for both append-only and lookup proofs.
Our logs can be used to secure the public key infrastructures that are crucial for secure web browsing and for end-to-end encrypted messaging.
Furthermore, our logs can help secure the currently-feeble software distribution ecosystem, where users can be easily tricked into downloading malicious binaries.
Unfortunately, our log's polylogarithmic (de)amortized append time is not yet fast enough for practice and we hope to speed it up in future work.
Similarly, (some of) our concrete proof sizes could also be further reduced in future work.

At the core of almost all constructions in this thesis lie new techniques for computing proofs fast in constant-sized polynomial commitments and in cryptographic accumulators.
We believe some of these techniques could be of independent interest.
For example, our authenticated multipoint evaluation tree (AMT) gives rise to a new vector commitment (VC) scheme, which can be used to scale cryptocurrencies.
